
Cover Sheet
========================================================


By including this statement, we, all the students listed in the table
below, declare that:

- We hold a copy of this assignment if the original is lost or damaged.

- We hereby certify that no part of this assignment has been copied from
  any other student's work or from any other source except where due
  acknowledgement is made in the assignment.

- No part of the assignment has been written for us by any other person
  except where collaboration has been authorised by the unit coordinator.

- We are aware that this work may be reproduced and submitted to plagiarism
  detection software programs for the purpose of detecting possible
  plagiarism; this software may retain a copy on its database for future
  plagiarism checking.

- We hereby certify that no part of this assignment or product has been
  submitted by any of us in another (previous or current) assessment, except
  where appropriately referenced, and with prior permission from the unit
  coordinator for this unit.

- We hereby certify that we have read and understand what the University
  considers to be academic misconduct, and that we are aware of the
  penalties that may be imposed for academic misconduct.

Name                  | Student Number  | Contribution (%)
----------------------|-----------------|-----------------
Rachel Hardie         |  18820821       |   25%
Dylan Wang            |  18998014       |   25%
Dylan Yoo             |  18640377       |   25%
Sreenath Ramachandran |  18878716       |   25%

<div style="page-break-before:always;"></div>

---
Title: "Analysis of J.K. Rowling"
output: html_document
---

##Introduction


This report examines and analyses the twitter language used by popular author J.K. Rowling and twitter users who interact with or mention her.


##Analysis of Twitter language about J.K. Rowling
In this section, we want to examine the language used in tweets. The rtweet package was used to to download 1000 tweets that contain the terms 'J.K. Rowling', rowling, and jk_rowling then save them as a .csv so as to not repeatedly call the api and because of the fast changing nature of twitter the frequent terms could change significantly. The terms we are analysing were captured on 28th September 2018. 

```{r message=FALSE, warning=FALSE}

library("ROAuth")
library("tm")
library("wordcloud")
library("rtweet")
library("twitteR")
library("wordcloud2")
#install.packages("dendextend")
library("dendextend")
library("knitr")

##Code below was used to create the SWA project.csv file,
## which is used for the work to have a consistent set of tweets for analysis.

#key="3g0mNQkwVxe0JKiRfSyyS0rvu"
#secret="Wu38XdVVJFPWpqWVBQDwyl2Reqhmg8XhDWjTJl3XwOqNlwYEcx"
#access_token="243587433-BPMCMRHSyb3pSJS3raa0w9qPCU3RAnB3aPZtjVEM"
#access_secret="g8iN8UChw7jAnybFKfMxPWiWiS8hZw1lVeKzmipnnu3zR"
#app="WSU300958"
#setup_twitter_oauth(key,secret,access_token,access_secret)
#tweets=search_tweets(q="'J.K.Rowling' OR Rowling OR jk_rowling",n=1000,lang="en")
#save_as_csv(tweets,"SWAProject.csv")
tweets=read.csv("SWAProject.csv")
```

We then constructed a document-term matrix using TFIDF weighting to describe the frequency of terms in the tweets we had collected.

```{r results='hide', message=FALSE, warning=FALSE}
corpus=Corpus(VectorSource(tweets$text))
corpus = tm_map(corpus, function(x) iconv(x, to = 'UTF8', sub = 'byte'))
corpus = tm_map(corpus, function(x) iconv(x, to = 'ASCII', sub = ' '))
corpus = tm_map(corpus,removeNumbers)
corpus = tm_map(corpus, removeWords,c(stopwords(),"J.K. Rowling","https", "t.co"))
corpus = tm_map(corpus,removePunctuation)
corpus = tm_map(corpus,stripWhitespace)
corpus = tm_map(corpus, tolower)
corpus = tm_map(corpus, stemDocument)
corpus = tm_map(corpus, removeWords,c(stopwords(),"jk","https", "t.co","rowl","jkrowl","will","like","just","doe","far","quot","look","take","make","jaqkcpmtg","ygorfremo","ask","peopl","next","twitter","peopl","new","write","charact","got","ohhgmljqrm","say","defend","respond", "vrmgsnrsa","bbepgeik","nkuwxgsn","novrijqr","nlrbgguhxt"))

dtm = DocumentTermMatrix(corpus)
tweet.wdtm = weightTfIdf(dtm)
tweet.matrix = as.matrix(tweet.wdtm)

```


After removing non-informative words we sum the frequencies of each terms in all documents to obtain a vector of term frequencies summed over all tweets then visualised the frequency of words in a word cloud.

```{r}
##term frequencies are stored in the vector 'freqs'
freqs=colSums(tweet.matrix)
data = data.frame(names(freqs), freqs)
wordcloud2(data, size = 0.3, shape = "circle")

head(freqs)
```

Then we Compute the proportion of each term in the tweets from the vector of term frequencies and Visualize the top 20 words and their proportion by using a bar plot.
```{r}
id=order(freqs,decreasing = TRUE)[1:20]
topWords=colnames(tweet.matrix)[id]
N = length(freqs)
words.proportion = freqs/N
barplot(words.proportion[id], col=heat.colors(20),las=2)
```

In order to visualise the clustering of words we created a a single linkage and complete linkage dendrogram of the 40 most frequent terms.
         
```{r}
id2 = order(freqs, decreasing = TRUE)[1:40]
topWords.clus = colnames(tweet.matrix)[id2]
 D = dist(freqs[id2])
 
##Complete Linkage 
h.complete = hclust(D)
h.complete <- color_branches(h.complete, k = 5)
plot(h.complete,main = "Complete")

##Single Linkage
h.single = hclust(D, method="single")
h.single <- color_branches(h.single, k = 5)
plot(h.single,main = "Single")

```

After review, we concluded that Complete Linkage is the better option as the clusters are better defined and it does not suffer from clusters being forced together due to single elements which, specifically for these tweets, is important because some terms such as the titles of books and movies written by or based on the works of J.K. Rowling can cause there to be different clusters linked together. This is known as chaining phenomena and can cause clusters to have a large diameter, wheras complete linkage will give us clusters with a more equal diameter.
 

##What do these words tell us about the Person? Comment on what people are saying about this person? 

The majority of terms are related more to the creations of J.K. Rowling than about her personally. Actors are frequently mentioned in relation to her, most likely because she is involved with the production of major motion pictures based on her written works. There is also a significant cluster regarding the upcoming film, 'Fantastic Beasts and Where To Find Them: The Crimes of Grindelwald' and a Korean Actress.

# Clustering the Users Who Posted Tweets About the Public Figure

We want to categorize (cluster) the users of the tweets about J.K. Rowling based on the descriptions provided in their Twitter account to figure out what kind of users are tweeting about them. Descriptions in the users' Twitter profiles give a short piece of information about the Twitter handle. To cluster users we built a document term matrix by using the user descriptions of the tweets.

We used K-means clustering with cosine distance for better clustering. First a Distance matrix was required to find cosine distance then we performed MDS using 300 dimensions

```{r}
corpus1=Corpus(VectorSource(tweets$description))
corpus1 = tm_map(corpus1, function(x) iconv(x, to = 'UTF8', sub = 'byte'))
corpus1 = tm_map(corpus1, function(x) iconv(x, to = 'ASCII', sub = ' '))
corpus1 = tm_map(corpus1,removeNumbers)
corpus1 = tm_map(corpus1, removeWords,c(stopwords()))
corpus1 = tm_map(corpus1,removePunctuation)
corpus1 = tm_map(corpus1,stripWhitespace)
corpus1 = tm_map(corpus1, tolower)
corpus1 = tm_map(corpus1, stemDocument)
descriptionDtm = DocumentTermMatrix(corpus1)
tweet.wdescriptionDtm = weightTfIdf(descriptionDtm)
tweet.descriptionmatrix = as.matrix(tweet.wdescriptionDtm)
#removing profiles with no description.
empties = which(rowSums(abs(tweet.descriptionmatrix)) == 0)
tweet.descriptionmatrix = tweet.matrix[-empties, ]

#We are using Kmeans clustering with cosine distance for better clustering.
#Distance matrix is required to find cosine distance.
norm.tweet.matrix = diag(1/sqrt(rowSums(tweet.descriptionmatrix^2))) %*% tweet.descriptionmatrix
D = dist(norm.tweet.matrix, method = "euclidean")^2/2
D[is.na(D)]=0# Convert na's in the distance matrix to 0.
## perform MDS using 300 dimensions
mds.tweet.matrix <- cmdscale(D, k=300)
##Elbow
SSW = rep(0,15)
for (i in 1:15) {
  number.of.clusters=i
  k=kmeans(mds.tweet.matrix,number.of.clusters,nstart = 10)
  SSW[i]=k$tot.withinss
}
plot(1:15,SSW,type="b")
## After inspecting the plot we are selecting the number of clusters= 5  using the elbow method.

```
 After inspecting the plot we used the elbow method to selected the number of clusers to be five.

Users were then clustered and visualised in two-dimensional vecor space.
```{r}
#K means clustering using cosine distance and number of clusters obtained from the elbow method.
K = kmeans(mds.tweet.matrix,5, nstart = 10 )
tweet.matrix.2d = cmdscale(D,k=2)
plot(tweet.matrix.2d, col = K$cluster)
```

We listed the top 10 words associated with each user cluster then manually determined the type of user profiles for each cluster (e.g. journalist, organisation, personal).

Cluster 1
```{r echo=FALSE}
print("Cluster 1:")
cluster.number = 1
clusterTweetsId = which(K$cluster == cluster.number)
clusterTweets = tweet.matrix[clusterTweetsId,]
clusterTermWeight = colMeans(clusterTweets)
sort(clusterTermWeight, decreasing = TRUE)[1:10]
tweets1=tweets[clusterTweetsId,]#Look manually at the user profiles to find the type of user profiles.
```
Cluster 2
```{r echo=FALSE}
print("Cluster 2:")
cluster.number2 = 2
clusterTweetsId2 = which(K$cluster == cluster.number2)
clusterTweets2 = tweet.matrix[clusterTweetsId2,]
clusterTermWeight2 = colMeans(clusterTweets2)
sort(clusterTermWeight2, decreasing = TRUE)[1:10]
tweets2=tweets[clusterTweetsId2,]#Look manually at the user profiles to find the type of user profiles.
```

Cluster 3
```{r echo=FALSE}
print("Cluster 3:")
cluster.number3 = 3
clusterTweetsId3 = which(K$cluster == cluster.number3)
clusterTweets3 = tweet.matrix[clusterTweetsId3,]
clusterTermWeight3 = colMeans(clusterTweets3)
sort(clusterTermWeight3, decreasing = TRUE)[1:10]
tweets3=tweets[clusterTweetsId3,]#Look manually at the user profiles to find the type of user profiles.
```

Cluster 4
```{r echo=FALSE}
print("Cluster 4:")
cluster.number4 = 4
clusterTweetsId4 = which(K$cluster == cluster.number4)
clusterTweets4 = tweet.matrix[clusterTweetsId4,]
clusterTermWeight4 = colMeans(clusterTweets4)
sort(clusterTermWeight4, decreasing = TRUE)[1:10]
tweets4=tweets[clusterTweetsId4,]#Look manually at the user profiles to find the type of user profiles.
```

Cluster 5
```{r echo=FALSE}
print("Cluster 5:")
cluster.number5 = 5
clusterTweetsId5 = which(K$cluster == cluster.number5)
clusterTweets5 = tweet.matrix[clusterTweetsId5,]
clusterTermWeight5 = colMeans(clusterTweets5)
sort(clusterTermWeight5, decreasing = TRUE)[1:10]
tweets5=tweets[clusterTweetsId5,]#Look manually at the user profiles to find the type of user profiles.
```

4.    Comment on your findings.

```{r}


```

8.3 Retweet Analysis of the User Clusters
We want to examine if the number of retweeted tweets is independent of which user cluster posted the tweet.

1.       Find the tweets of the users at each cluster at your tweets file and examine how many of them are retweeted.
```{r}
retweetsId=which(tweets[clusterTweetsId,]$is_retweet==TRUE)
##38 out of 53 tweets in cluster 1 are retweets.
retweetsId2=which(tweets[clusterTweetsId2,]$is_retweet==TRUE)
##45 out of 79 Tweets in cluster 2 are retweets.
retweetsId3=which(tweets[clusterTweetsId3,]$is_retweet==TRUE)
##18 out of 22 Tweets in cluster 3 are retweets.
retweetsId4=which(tweets[clusterTweetsId4,]$is_retweet==TRUE)
##462 out of 676 Tweets in cluster 4 are retweets.
retweetsId5=which(tweets[clusterTweetsId5,]$is_retweet==TRUE)
##18 out of 27 tweets in cluster 5 are retweets.

```

2.      Construct a 2×M table where M is the number of user clusters you found at Section 2. Each row (2 rows in total) should represent the total number of retweeted tweets and non-retweeted tweets in each cluster.
```{r}
#Number of retweeted tweets in each cluster.
R=length(retweetsId)
R2=length(retweetsId2)
R3=length(retweetsId3)
R4=length(retweetsId4)
R5=length(retweetsId5)
## Number of tweets which are not retweeted in each cluster
NR=length(clusterTweetsId)-R
NR2=length(clusterTweetsId2)-R2
NR3=length(clusterTweetsId3)-R3
NR4=length(clusterTweetsId4)-R4
NR5=length(clusterTweetsId5)-R5

comparison.table = matrix(c(R,R2,R3,R4,R5,NR,NR2,NR3,NR4,NR5),ncol = 5,byrow = TRUE)
colnames(comparison.table)=c("Cluster1","Cluster2","Cluster3","Cluster4","Cluster5")
rownames(comparison.table)=c("Retweets","Not Retweets")
comparison.table=as.table(comparison.table)
comparison.table
```
3.      Is retweeting independent of user groups? Perform an appropriate test to answer this question.
```{r}
#Chi-sq test for Independence
table.matrix=as.matrix(comparison.table)
stretchTable=function(tab,variableNames){
  tabx=rep(rownames(tab),rowSums(tab))
  l=ncol(tab)
  m=nrow(tab)
  cn=colnames(tab)
  taby=c()
  for(a in 1:m){
    for(b in 1:l){
      taby=c(taby,rep(cn[b],tab[a,b]))
    }
  }
  d=data.frame(x=tabx,y=taby)
  colnames(d)=variableNames
  return(d)
}
tab2= stretchTable(table.matrix,c("Tweets","Cluster"))
table(tab2)
 expectedIndependent = function(X) {
    n = sum(X)
    p = rowSums(X)/sum(X)
   q = colSums(X)/sum(X)
    return(p %o% q * n) # outer product creates table
 }
 chiSquaredStatistic = function(X, E) {
     return(sum((X-E)^2/E))
 }
 
  ## compute the expected table
 E = expectedIndependent(table(tab2)) # compute expected counts 
 
 ## compute the randomisation distribution
 x2dist = replicate(1000, { # compute 1000 randomised chi-squared statistics
   clusterShuffle = sample(tab2$Cluster)
  tweetShuffle = sample(tab2$Tweets)
  Xindep = table(tweetShuffle, clusterShuffle)
   chiSquaredStatistic(Xindep, E)
 })
 hist(x2dist)
 x2 = chiSquaredStatistic(table(tab2), E)
 print(x2)
 pval = mean(x2dist > x2)
 print(pval)
 
 #conclusion
#Ho= retweets and clusters are independent
#Ha= retweets and clusters are not independent
# calculate pvalue
p.value=mean(x2dist>x2)
p.value
# Do not reject null nypothesis as pvalue>alpha(0.05)
#As the pvalue is greater than the significance level do not reject the null hypothesis.
#We do not have enough evidence to suggest that the retweets and clusters are not independent.
```
4.      Interpret your results in context.
```{r}

```
By combining all your findings, what can we say about the person's image on Twitter? Draw a conclusion from your report.

The person wants the above three parts of analysis to be written up in a professional report. Each part should have its own section of the report and all questions should have thoughtful answers. Include only the relevant piece of code along with its output in the body of your assignment. More detailed code should be in the Appendix part of the assignment.
